Equations & R Code

### 2017-03-20 manuscript/coexistence-stability_ms.Rmd
min9or update of code with rounding

The gap between theoretical expectations and empirical results of diversity--\new{ecosystem variability} relationships might reflect the divergence of theory developed to explain species coexistence and theory developed to explain diversity and ecosystem variability.
\new{In his thorough review of the topic, Loreau (2010) cautions that "one of the pieces of the stability jigsaw that is still missing here is the interconnection between community stability and the maintenance of species diversity due to temporal environmental variability."}
One reason these two disciplines have diverged is because they have focused on different questions.
Diversity--\new{ecosystem variability} studies typically ask how ecosystem variability responds to different levels of species richness at a given level of environmental variability [reviewed in @Kinzig2001; @Loreau2010], whereas coexistence studies ask how species richness responds to different levels of environmental variability [@Chesson1981a].

>>>>

The gap between theoretical expectations and empirical results of diversity--\new{ecosystem variability} relationships might reflect the divergence of theory developed to explain species coexistence and theory developed to explain diversity and ecosystem variability.
\new{In his thorough review of the topic, Loreau (2010) cautions that "one of the pieces of the stability jigsaw [puzzle] that is still missing here is the interconnection between community stability and the maintenance of species diversity due to temporal environmental variability."}
One reason these two disciplines have diverged is because they have focused on different questions.
Diversity--\new{ecosystem variability} studies typically ask how ecosystem variability responds to different levels of species richness at a given level of environmental variability [reviewed in @Kinzig2001; @Loreau2010], whereas coexistence studies ask how species richness responds to different levels of environmental variability [@Chesson1981a].

### 2017-03-20 manuscript/coexistence-stability_ms.tex
min9or update of code with rounding

The gap between theoretical expectations and empirical results of
diversity--\new{ecosystem variability} relationships might reflect the
divergence of theory developed to explain species coexistence and theory
developed to explain diversity and ecosystem variability.
\new{In his thorough review of the topic, Loreau (2010) cautions that "one of the pieces of the stability jigsaw that is still missing here is the interconnection between community stability and the maintenance of species diversity due to temporal environmental variability."}
One reason these two disciplines have diverged is because they have
focused on different questions. Diversity--\new{ecosystem variability}
studies typically ask how ecosystem variability responds to different
levels of species richness at a given level of environmental variability
(reviewed in Kinzig et al. 2001; Loreau 2010), whereas coexistence
studies ask how species richness responds to different levels of
environmental variability (Chesson \& Warner 1981).

@@

\hypertarget{ref-DeClerck2006}{}
DeClerck, F.A.J., Barbour, M.G. \& Sawyer, J.O. (2006). Species richness
and stand stability in conifer forests of the Sierra Nevada.
\emph{Ecology}, 87, 2787--2799.

>>>>

The gap between theoretical expectations and empirical results of
diversity--\new{ecosystem variability} relationships might reflect the
divergence of theory developed to explain species coexistence and theory
developed to explain diversity and ecosystem variability.
\new{In his thorough review of the topic, Loreau (2010) cautions that "one of the pieces of the stability jigsaw [puzzle] that is still missing here is the interconnection between community stability and the maintenance of species diversity due to temporal environmental variability."}
One reason these two disciplines have diverged is because they have
focused on different questions. Diversity--\new{ecosystem variability}
studies typically ask how ecosystem variability responds to different
levels of species richness at a given level of environmental variability
(reviewed in Kinzig et al. 2001; Loreau 2010), whereas coexistence
studies ask how species richness responds to different levels of
environmental variability (Chesson \& Warner 1981).

@@

\hypertarget{ref-DeClerck2006}{}
DeClerck, F.A.J., Barbour, M.G. \& Sawyer, J.O. (2006). SPECIES RICHNESS
AND STAND STABILITY IN CONIFER FORESTS OF THE SIERRA NEVADA.
\emph{Ecology}, 87, 2787--2799.
